---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
devtools::install_github("Orrslab/popClumpTestR")
library(popClumpTestR)
```

# Introduction

Enables simulating X-Y population point data to test robustness of methods to recognize clumpedness. Given Quantification Methods (QMs), it is possible to simulate many populations at different levels of clumping. Afterwards, it is possible to generate Large Random-like Population Distributions (LRPDs) of your QMs - a baseline for random populations of 100 individuals in high spatial randomness, enabling a distribution per CM of random values. A high percentile per CM is marked as a Minimum Non-Random Threshold (MNRT), and a Non-Random Percent (NRP) of the simulation data is then calculated. Display functions (using ggplot2) then enable to qualitatvely ascertain which CMs are good enough, with differentiability of NRPs at different levels of clumping, and also to ascertain a minimum sample size.
Note that the locations of simulations and example data are in Israel Transverse Mercator (ITM) - https://en.wikipedia.org/wiki/Israeli_Transverse_Mercator. This is to simulate localized coordinates - but technically any localized coordinate system will do.

# Process

1.  Create some R file with all your clumping methods (CMs) and helper functions - CMs used in the paper are available below

```{r, eval=FALSE}
library(spatstat)

transform_df_to_ppp <- function(individual.locations.data.frame, polygons) {
  pts <- individual.locations.data.frame[,c('X','Y')]
  ##sp::coordinates(pts) <- ~X+Y
  
  pts <- sfheaders::sf_point(pts)
  
  ## spatstat polygons is expected to be reversed
  wanted_poly<-cbind(rev(sf::st_coordinates(polygons[[1]])[,1]),rev(sf::st_coordinates(polygons[[1]])[,2]))
  
  ppps <- ppp(sf::st_coordinates(pts)[,1],sf::st_coordinates(pts)[,2],poly=wanted_poly)
  
  return(ppps)
}

ripleys.k <- function(individual.locations.data.frame, polygons, n.for.calc) {
  A <- sum(unlist(lapply(polygons, function(x) sf::st_area(x))))
  n <- length(individual.locations.data.frame$X)
  r <- 0.5 * ( A/ n)^ 0.5 
  ppps <- transform_df_to_ppp(individual.locations.data.frame, polygons)
  ret<-spatstat.explore::Kest(ppps, r = c(0,r), correction = 'isotropic')
  retval <- ret$iso[2]/(pi*r^2)
  return(retval)
}

ripleys.k.natural <- function(individual.locations.data.frame, polygons, n.for.calc){
  
  A <- sum(unlist(lapply(polygons, function(x) sf::st_area(x))))
  n <- length(individual.locations.data.frame$X)
  r <- ( A/ n)^ 0.5 
  mult <- A/n^2
  k <- 0
  
  for(i in 1:(length(individual.locations.data.frame$X)-1)){
    p1 <- individual.locations.data.frame[i,]
    for(j in (i+1):length(individual.locations.data.frame$X)){
      p2 <- individual.locations.data.frame[j,]
      curr_dist <- ((p1$X-p2$X)^2 + (p1$Y-p2$Y)^2)^0.5
      if(curr_dist<=r){
        k <- k+1
      }
    }
  }
  
  k<-k/n
  
  return(k)
}

ripleys.k.uniform.dist <- function(individual.locations.data.frame, polygons, n.for.calc){
  
  A <- sum(unlist(lapply(polygons, function(x) sf::st_area(x))))
  n <- length(individual.locations.data.frame$X)
  r <- ( A/ n)^ 0.5 
  mult <- A/(n*(n-1))
  k <- 0
  
  study_area <- sf::st_union(do.call(c, polygons))  
  
  for(i in 1:length(individual.locations.data.frame$X)){
    p1 <- individual.locations.data.frame[i,]
    
    p <- sf::st_sfc(
      sf::st_point(c(p1$X, p1$Y)),
      crs = sf::st_crs(study_area)
    )
    
    circle <- sf::st_buffer(p, r)
    
    A_i <- as.numeric(sf::st_area(
      sf::st_intersection(circle, study_area)
    ))
    
    for(j in 1:length(individual.locations.data.frame$X)){
      if(i!=j){
        p2 <- individual.locations.data.frame[j,]
        curr_dist <- ((p1$X-p2$X)^2 + (p1$Y-p2$Y)^2)^0.5
        if(curr_dist<=r){
          k <- k+1/A_i
        }
      }
    }
  }
  
  k<-mult*k
  
  return(k)
}


ripleys.k.rand.dist <- function(individual.locations.data.frame, polygons, n.for.calc){
  
  A <- sum(unlist(lapply(polygons, function(x) sf::st_area(x))))
  n <- length(individual.locations.data.frame$X)
  r <- 0.5 * ( A/ n)^ 0.5 
  mult <- A/(n*(n-1))
  k <- 0
  
  study_area <- sf::st_union(do.call(c, polygons))  
  
  for(i in 1:length(individual.locations.data.frame$X)){
    p1 <- individual.locations.data.frame[i,]
    
    p <- sf::st_sfc(
      sf::st_point(c(p1$X, p1$Y)),
      crs = sf::st_crs(study_area)
    )
    
    circle <- sf::st_buffer(p, r)
    
    A_i <- as.numeric(sf::st_area(
      sf::st_intersection(circle, study_area)
    ))
    
    for(j in 1:length(individual.locations.data.frame$X)){
      if(i!=j){
        p2 <- individual.locations.data.frame[j,]
        curr_dist <- ((p1$X-p2$X)^2 + (p1$Y-p2$Y)^2)^0.5
        if(curr_dist<=r){
          k <- k+1/A_i
        }
      }
    }
  }
  
  k<-mult*k
  
  return(k)
}

clark.evans.median <- function(individual.locations.data.frame, polygons, n.for.calc) {
  ppps <- transform_df_to_ppp(individual.locations.data.frame, polygons)
  clarkevans.res <- spatstat.explore::clarkevans(ppps)
  
  ce.by.mean <- clarkevans.res[1]
  
  nndists <- spatstat.geom::nndist(ppps)
  mean.nndist <- mean(nndists)
  median.nndist <- median(nndists)
  
  ret <- -median.nndist * ce.by.mean / mean.nndist
  
  
  return(ret)
}

clark.evans.trimmed.mean <- function(individual.locations.data.frame, polygons, n.for.calc) {
  ppps <- transform_df_to_ppp(individual.locations.data.frame, polygons)
  clarkevans.res <- spatstat.explore::clarkevans(ppps)
  
  ce.by.mean <- clarkevans.res[1]
  
  cutoff <- 0.96 # make sure not divisible
  
  nndists <- sort(spatstat.geom::nndist(ppps))
  mean.nndist <- mean(nndists)
  
  end <- min(length(nndists)-1,round(cutoff*length(nndists)))
  
  nndists.cutoff <- nndists[1:end]
  nndists.cutoff.mean <- mean(nndists.cutoff)

  ret <- -nndists.cutoff.mean * ce.by.mean / mean.nndist
  
  
  return(ret)
}

clark.evans.ses <- function(individual.locations.data.frame, polygons, n.for.calc) {
  ppps <- transform_df_to_ppp(individual.locations.data.frame, polygons)
  
  nndists <- spatstat.geom::nndist(ppps)
  
  area <- sf::st_area(polygons[[1]])
  
  exp.sd <- sqrt(area/nrow(individual.locations.data.frame))/sqrt(2) ## CE divides it by 2, so root 2 is sd
  exp.mean <- sqrt(area/nrow(individual.locations.data.frame))/2
  
  ret <- -(mean(nndists) - exp.mean) / exp.sd
  
  
  return(ret)
}

clark.evans.sd <- function(individual.locations.data.frame, polygons, n.for.calc) {
  ppps <- transform_df_to_ppp(individual.locations.data.frame, polygons)
  
  nndists <- spatstat.geom::nndist(ppps)
  
  area <- sf::st_area(polygons[[1]])
  
  dist <- sqrt(area/nrow(individual.locations.data.frame))/sqrt(2) ## CE divides it by 2, so root 2 is sd
  
  ret <-  sd(nndists) / dist
  
  
  return(ret)
}

clark.evans.sd <- function(individual.locations.data.frame, polygons, n.for.calc) {
  ppps <- transform_df_to_ppp(individual.locations.data.frame, polygons)
  
  nndists <- spatstat.geom::nndist(ppps)
  
  area <- sf::st_area(polygons[[1]])
  
  dist <- sqrt(area/nrow(individual.locations.data.frame))/sqrt(2) ## CE divides it by 2, so root 2 is sd
  
  ret <-  sd(nndists) / dist
  
  
  return(ret)
}

clark.evans.trimmed.sd <- function(individual.locations.data.frame, polygons, n.for.calc) {
  ppps <- transform_df_to_ppp(individual.locations.data.frame, polygons)
  
  cutoff <- 0.96 # make sure not divisible
  
  nndists <- sort(spatstat.geom::nndist(ppps))

  end <- min(length(nndists)-1,round(cutoff*length(nndists)))
  
  nndists.cutoff <- nndists[1:end]
  
  area <- sf::st_area(polygons[[1]])
  
  dist <- sqrt(area/nrow(individual.locations.data.frame))/sqrt(2) ## CE divides it by 2, so root 2 is sd
  
  ret <- sd(nndists.cutoff)/dist
  
  
  return(ret)
}

nfun <- function(individual.locations.data.frame, polygons, n.for.calc) {
  ppps <- transform_df_to_ppp(individual.locations.data.frame, polygons)
  
  nndists <- spatstat.geom::nndist(ppps)
  
  area <- sf::st_area(polygons[[1]])
  
  dist <- sqrt(area/nrow(individual.locations.data.frame))/2 ## CE divides it by 2!
  
  val_of_min <- (max(nndists)-min(nndists))/mean(nndists)
  val <- sum(val_of_min > 1.5)/length(nndists)
  
  val <- abs(mean(nndists) - median(nndists))
  
  return(val_of_min)
}


clump.pct <- function(individual.locations.data.frame, polygons, n.for.calc) {
  ppps <- transform_df_to_ppp(individual.locations.data.frame, polygons)
  
  nndists <- spatstat.geom::nndist(ppps)
  
  area <- sf::st_area(polygons[[1]])
  
  dist <- sqrt(area/nrow(individual.locations.data.frame))/2 ## CE divides it by 2!
  
  ret <- sum(nndists <= dist) / length(nndists)
  
  
  return(ret)
}

clark.evans.naive <- function(individual.locations.data.frame, polygons, n.for.calc) {
  ppps <- transform_df_to_ppp(individual.locations.data.frame, polygons)
  clarkevans.res <- spatstat.explore::clarkevans(ppps)
  return(-clarkevans.res[1])
}

clark.evans.naive.orig <- function(individual.locations.data.frame, polygons, n.for.calc) {
  ppps <- transform_df_to_ppp(individual.locations.data.frame, polygons)
  clarkevans.res <- spatstat.explore::clarkevans(ppps)
  return(clarkevans.res[1])
}

clark.evans.cdf <- function(individual.locations.data.frame, polygons, n.for.calc) {
  ppps <- transform_df_to_ppp(individual.locations.data.frame, polygons)
  clarkevans.res <- spatstat.explore::clarkevans(ppps)
  return(-clarkevans.res[2])
}

quadrat.test.statistic <- function(individual.locations.data.frame, polygons, n.for.calc) {
  ppps <- transform_df_to_ppp(individual.locations.data.frame, polygons)
  
  if(n.for.calc == 0 ){
    n.for.calc <- nrow(individual.locations.data.frame)
  }
  qtest<-spatstat.explore::quadrat.test(ppps,method='M', nx=floor(sqrt(n.for.calc)), ny=floor(sqrt(n.for.calc)))
  
  return(qtest$p.value)
}

nndist.test.tailored <- function(individual.locations.data.frame, polygons, n.for.calc) {
  ppps <- transform_df_to_ppp(individual.locations.data.frame, polygons)
  
  if(n.for.calc == 0 ){
    n.for.calc <- nrow(individual.locations.data.frame)
  }
  
  nndists <- spatstat.geom::nndist(ppps)
  
  exp.dist <- sqrt(sf::st_area(polygons[[1]])/nrow(individual.locations.data.frame))
  
  dists <- c()
  
  for(i in 1:(nrow(individual.locations.data.frame)-1)){
    ind.1 <- individual.locations.data.frame[i,]
    for(j in (i+1):nrow(individual.locations.data.frame)){
      ind.2 <- individual.locations.data.frame[j,]
      dist <- sqrt((ind.1$X-ind.2$X)^2+(ind.1$Y-ind.2$Y)^2)
      dists <- c(dists, dist)
    }
  }
  
  nnndists <- dists[!dists %in% nndists]

  alpha.nnndists <- (mean(nnndists)^2)/var(nnndists)
  theta.nnndists <- var(nnndists)/mean(nnndists)
  
  alpha.dists <- (mean(dists)^2)/var(dists)
  theta.dists <- var(dists)/mean(dists)
  
  
  return(mean(nnndists)/mean(nndists))
}

quadrat.test.tailored <- function(individual.locations.data.frame, polygons, n.for.calc) {
  ppps <- transform_df_to_ppp(individual.locations.data.frame, polygons)

  if(n.for.calc == 0 ){
    n.for.calc <- nrow(individual.locations.data.frame)
  }
  qcount<- as.data.frame(spatstat.geom::quadratcount(ppps, nx=floor(sqrt(n.for.calc)), ny=floor(sqrt(n.for.calc))))

  ratio.zero.quadrats <- sum(qcount$Freq %in% 0)/nrow(qcount)
  
  val <- 1-min(mean(qcount$Freq)/var(qcount$Freq),1)
  
  return(ratio.zero.quadrats)
}

exp.dist.cnt <- function(individual.locations.data.frame, polygons, n.for.calc) {
  
  nndists <- c()
  fndists <- c()
  
  exp.dist <- sqrt(sf::st_area(polygons[[1]])/nrow(individual.locations.data.frame))
  
  for(i in 1:length(individual.locations.data.frame$X)){
    p1 <- individual.locations.data.frame[i,]
    curr.min <- NaN
    curr.max <- NaN
    for(j in 1:length(individual.locations.data.frame$X)){
      if(i==j) next
      p2 <- individual.locations.data.frame[j,]
      curr_dist <- ((p1$X-p2$X)^2 + (p1$Y-p2$Y)^2)^0.5
      
      if(is.nan(curr.min) || curr.min > curr_dist){
        curr.min <- curr_dist
      }
      
      if(is.nan(curr.max) || curr.max < curr_dist){
        curr.max <- curr_dist
      }
    }
    nndists <- c(nndists, curr.min)
    fndists <- c(fndists, curr.max)
  }
  
  return(1-mean(nndists)/mean(fndists))
}
```

2.  Create polygon list for your simulation - example using bird.location.data below

```{r, eval=FALSE}
l63 <- bird.location.data[bird.location.data$POPULATION == 'Spur-winged Lapwing 63',]
  
polys <- generate_simulation_polygons(l63, use_bounding_rect = F)
  
```

3.  Create vector of the CM names and helper function names. Optional - test your CMs ahead of time to see if they are valid CMs

```{r, eval=FALSE}

  function_names = c(
    'ripleys.k',
    'clark.evans.naive',
    'clark.evans.naive',
    'clark.evans.trimmed.mean',
    'clark.evans.median',
    'clark.evans.cdf',
    'clump.pct'
    #'ripleys.k.natural',
    #'clark.evans.sd',
    #'clark.evans.trimmed.sd'
    #'quadrat.test.tailored'
    #'quadrat.test.statistic'
    #'nfun'
  )
  
  helper_funcs = c(
          'transform_df_to_ppp', 
          'ppp',
          'nndist'
          )
  
  check_clumping_method_validity(polys, 'ripleys.k')
```

4.  Suggested - run simulation process + LRPD process on a small Initial sample size (ISS) + large jumps in Degree of Clumping (DOC, suggested 20) + large jump in removed individuals per level (suggested around 5 individuals per level) + 100 repetitions. This is to test generally if your CM is a good one, and merits running on finer levels.

```{r, eval=FALSE}
set.seed(45)

wanted.sim.type <- simulation_type$uniform.to.random ## for example, see types
wanted.uniform.generation.type <- uniform_random_generation_type$split.polygon.and.generate.separately

  
start = Sys.time()
heatmap.data<-simulate_population_remove_from_original_for_smaller_pops(
  polys,   
  function_names,                                                               
  helper_funcs,
  sim.type = wanted.sim.type, ## wanted simulation type
  uniform.random.generation.type = wanted.uniform.generation.type, ## for uniform end if used
  uniform.noise.ratio = 0.1, ## noise for uniform generation if relevant
  initial_n = 30, # ISS
  percent_random_rise = 20, # DOC (Degree of clumping). 20 means 6 levels - 100%, 80%, 60%, 40%, 20%, and 0% clumped.
  delt_n = 5, # Number of Individuals to remove per level   
  simulations_per_percent = 100, # Repetitions per ISS + DOC
  recalculate_poly=T, #recalculate polygon for remaining individuals at each step
  recalculate_poly_with_rect=F, #use the real MCP and not the bounding rect
  plotResults = F, # Whether to display some of the populations 
  ns_to_plot = c(30), #if above is set to TRUE, which Current Sample Size (CSS) to display
  initial_div = 2, ## optional control parameter - closeness of individuals within clumps                                 
  n_clumps = 0, ## optional control parameter - number of clumps. Default for 0 is sqrt(ISS)
  n_cores = 0 ## default - use all but one of physical cores
  )

end = Sys.time()
print('Initial simulation generation took:')
print(end-start)

  
heatmap.to.use <- heatmap.data
  
n.for.calc <- max(heatmap.to.use$css) ## to set baseline level of clumping for the potentially larger LRPDs (100 individuals by default)
  
start = Sys.time()
lrpd.data <- generate_large_randomlike_population_distribution(polys,
                                                function_names,
                                                helper_funcs,
                                                sim.type = wanted.sim.type,
                                                uniform.random.generation.type = wanted.uniform.generation.type
                                                uniform.noise.ratio = 0.1,
                                                n.for.calc = n.for.calc,
                                                n.for.clumping = n.for.calc,
                                                max_pct_to_use=20, 
                                                percent_random_rise = 5,
                                                simulations_per_percent=100,
                                                recalculate_poly=T, #recalculate polygon for remaining individuals at each step
                                                recalculate_poly_with_rect=F, #use the real MCP and not the bounding rect
                                                n_cores = 0 ## default - use all but one of physical cores
                                                )
  
lrpd.to.use <- lrpd.data
end = Sys.time()
print('Initial LRPD generation took:')
print(end-start)
```

5.  Display the data to ascertain if your CMs are good for the finer process which takes longer - various display options below.

```{r, eval=FALSE}
## Initial plots to understand general logic. Read documentation.
  heatmap_control_plots(heatmap.to.use, lrpd.to.use, wanted_n = 0, 
                        just_hist = F,
                        with_mnrt = T)
  
## aggregate simulation data and calculate NRP per CM with the MNRT of the LRPD.
  aggregated.nrp.data <- calculate_nonrandom_percent_on_heatmap_data(heatmap.to.use,lrpd.to.use,
                                                   upperPercentile=0.95,
                                                   d_cutoff = c(0, 5, 10, 15, 20))

  
## display function to decide which CM to continue with - read documentation
  plts <- plot_simulation_data(aggregated.nrp.data, 
                       ##wanted_ns = c(1:10),
                       wanted_ds = 20*0:5,
                       use.nrp = T,
                       doHeatmaps = T,  
                       doLinePlots = T, 
                       doFlippedLinePlots = F,
                       fname.in.title=T,
                       #AOI = NULL,
                       #AOI = c(7, 50, 30, 100),
                       AOI = c(7,-100,10,100),
                       linewidth.for.AOI = 1,
                       grep.pretty.name.non.random.percent = 'Rejection Rate',
                       linewidth.lineplot = 1,
                       lineplot.min.color = 'blue',
                       lineplot.max.color = 'red')
```

6.  Can now run the entire process with finer levels - more DOC and/or less removed individuals and/or more repetitions and/or higher ISS. Example below with DOC drops of 5%, 1 individual removed per level, ISS=30, and 100 repetitions. 
**Note:** runtime may be high despite parallelism. Have tested all number of cores on i7 - anything above 5 cores incurred similar runtime. Also tested on linux with PTHREAD instead - only sped up the coarser stage (step 4) from around 1.5 minutes to 40 seconds - finer stage took the same time. 
When done, can repeat step 5 to display at a finer level.

```{r, eval=FALSE}
set.seed(45)

wanted.sim.type <- simulation_type$uniform.to.random ## for example, see types
wanted.uniform.generation.type <- uniform_random_generation_type$split.polygon.and.generate.separately

  
start = Sys.time()
heatmap.data<-simulate_population_remove_from_original_for_smaller_pops(
  polys,   
  function_names,                                                               
  helper_funcs,
  sim.type = wanted.sim.type, ## wanted simulation type
    uniform.random.generation.type = wanted.uniform.generation.type, ## for uniform end if used
  uniform.noise.ratio = 0.1, ## noise for uniform generation if relevant
  initial_n = 30, # ISS
  percent_random_rise = 5, # DOC (Degree of clumping). 20 means 6 levels - 100%, 80%, 60%, 40%, 20%, and 0% clumped.
  delt_n = 1, # Number of Individuals to remove per level   
  simulations_per_percent = 100, # Repetitions per ISS + DOC
  recalculate_poly=T, #recalculate polygon for remaining individuals at each step
  recalculate_poly_with_rect=F, #use the real MCP and not the bounding rect
  plotResults = F, # Whether to display some of the populations 
  ns_to_plot = c(30), #if above is set to TRUE, which Current Sample Size (CSS) to display
  initial_div = 2, ## optional control parameter - closeness of individuals within clumps                                 
  n_clumps = 0, ## optional control parameter - number of clumps. Default for 0 is sqrt(ISS)
  n_cores = 0 ## default - use all but one of physical cores
  )

end = Sys.time()
print('Initial simulation generation took:')
print(end-start)

  
heatmap.to.use <- heatmap.data
  
n.for.calc <- max(heatmap.to.use$css) ## to set baseline level of clumping for the potentially larger LRPDs (100 individuals by default)
  
start = Sys.time()
lrpd.data <- generate_large_randomlike_population_distribution(polys,
                                                function_names,
                                                helper_funcs,
                                                sim.type = wanted.sim.type,
                                                  uniform.random.generation.type = wanted.uniform.generation.type, ## for uniform end if used
                                                uniform.noise.ratio = 0.1,
                                                n.for.calc = n.for.calc,
                                                n.for.clumping = n.for.calc,
                                                max_pct_to_use=20, 
                                                percent_random_rise = 5,
                                                simulations_per_percent=100,
                                                recalculate_poly=T, #recalculate polygon for remaining individuals at each step
                                                recalculate_poly_with_rect=F, #use the real MCP and not the bounding rect
                                                n_cores = 0 ## default - use all but one of physical cores
                                                )
  
lrpd.to.use <- lrpd.data
end = Sys.time()
print('Initial LRPD generation took:')
print(end-start)
```

7.  Optional - can use attached example data bird.location.data to compare your CMs with several helpful display functions.

```{r, eval=FALSE}
bird_data_with_values <- calculate_values_example_data(bird.location.data, function_names)

cutoffs_per_cm <- c(20, 9, 23, 7, 10) ## NOTE - need a cutoff for each CM, based on the smallest CSS (current sample size) for which your CM was still differentiable.

## various options for display here - read the documentation.
  plots_of_example_data(bird_data_with_values, lrpd.to.use, cutoffs_per_cm, 
                        withSimData = F, withGradient = F, numericCutoffsForGradient = c(-2.4,-1))
  
  
# validation of clumped-random half range
{
  library(ggplot2)
  
  pops.sim <- c()
  rand.vals <- c()
  uni.vals <- c()
  for(pop in unique(bird.location.data$POPULATION)) {
    
    p <- bird.location.data[bird.location.data$POPULATION==pop,]
    
    rect <- generate_simulation_polygons(p, use_bounding_rect = T)
    res<- lapply(1:1000,function(i) {
      pop <- generate_random_population(nrow(p),rect)
      polys2 <- generate_simulation_polygons(pop, use_bounding_rect = F)
      rand.val <- clark.evans.trimmed.mean(pop,polys2,0)
      rand.noise <- sample(5:25,1) / 100
      pop <- generate_uniform_population(nrow(p), rect, noise.ratio = rand.noise)
      polys2 <- generate_simulation_polygons(pop, use_bounding_rect = F)
      uniform.val <- clark.evans.trimmed.mean(pop,polys2,0)
      return(list(rand.val=rand.val, uniform.val=uniform.val))
    })
    
    # res<- lapply(1:1000,function(i) {
    #   #pop <- generate_random_population(nrow(p),rect)
    #   #polys2 <- generate_simulation_polygons(pop, use_bounding_rect = F)
    #   rand.noise <- sample(5:25,1) / 100
    #   pop <- generate_uniform_population(nrow(p), rect, noise.ratio = rand.noise)
    #   polys2 <- generate_simulation_polygons(pop, use_bounding_rect = F)
    #   dist <- sqrt(sf::st_area(polys2[[1]]) / nrow(p))
    #   return(dist)
    # })
    
    rand.vals.curr <- unlist(lapply(res, function(x) {x$rand.val}))
    uniform.vals.curr <- unlist(lapply(res, function(x) {x$uniform.val}))
    
    pops.sim <- c(pops.sim, rep(pop,1000))
    rand.vals <- c(rand.vals, rand.vals.curr)
    uni.vals <- c(uni.vals, uniform.vals.curr)
  }
  
  sim.results <- data.frame(pop=pops.sim, rand.vals=rand.vals, uniform.vals=uni.vals)
  
  rand.uni.pop.tests <- rbind(cbind('Random',sim.results[,c(1,2)]))
  colnames(rand.uni.pop.tests) <- c('type','pop','TMCEI')
  
  rand.uni.pop.tests.uni <- rbind(cbind('Uniform',sim.results[,c(1,3)]))
  colnames(rand.uni.pop.tests.uni) <- c('type','pop','TMCEI')
  
  rand.uni.pop.tests <- rbind(rand.uni.pop.tests, rand.uni.pop.tests.uni)
  
  pops <- c()
  val <- c()
  ps.rand <- c()
  ps.uni <- c()
  for(pop in unique(rand.uni.pop.tests$pop)) {
    
    p <-bird.location.data[bird.location.data$POPULATION == pop,]
    polys <- generate_simulation_polygons(p, use_bounding_rect = F)
    rect <- generate_simulation_polygons(p, use_bounding_rect = T)
    real.val <- clark.evans.trimmed.mean(p,polys,0)
    print(paste(pop, real.val))
    
    sub <- rand.uni.pop.tests[rand.uni.pop.tests$pop==pop,]
    rand.vals <- sub[sub$type=='Random',]$TMCEI
    uniform.vals <- sub[sub$type=='Uniform',]$TMCEI
    
    p.rand<-sum(rand.vals<real.val)/length(rand.vals)
    p.uni<-sum(uniform.vals<real.val)/length(uniform.vals)

    pops <- c(pops, pop)
    val <- c(val, real.val)
    ps.rand <- c(ps.rand,p.rand)
    ps.uni <- c(ps.uni,p.uni)

    plt <- ggplot(sub,aes(x=TMCEI, fill=type)) + geom_histogram() +
      geom_vline(xintercept = real.val) + labs(title=paste(pop,', p.rand=',round(p.rand,3),', p.uni=',round(p.uni,3))) + theme_classic()
    print(plt)
  }
    
  
  pop.rand.uni.comp.results <- data.frame(pop=pops,TMCEI=val,p.val.rand=ps.rand,p.val.uni=ps.uni)
}

```
